### 2025-09-24 paper/sec/evaluation.tex
[update] fix on table and on captions

\begin{figure}
    \centering
    \begin{subfigure}{0.48\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/success_rate_by_category}
        \caption{Success rate by testcases}
        \label{fig:success_rate_by_category}
    \end{subfigure}\hfill
    \begin{subfigure}{0.48\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/success_rate_by_category_count}
        \caption{Success rate by category count}
        \label{fig:success_rate_by_category_count}
    \end{subfigure}
    \caption{Comparison of success rates}
    \label{fig:success_rate_comparison}
\end{figure}

@@

    \centering
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{gpt4o}} & \multicolumn{2}{c}{\textbf{gpt5}} \\
            & \textbf{Success Rate} & \textbf{SD} & \textbf{Success Rate} & \textbf{SD} \\
            \hline
            Comparison     & 74   & 3 & 77.4 & 2 \\
            Data Retrieval & 76   & 3 & 77.4 & 2 \\
            Difference     & 80   & 3 & 77.4 & 2 \\
            Min/max        & 50   & 3 & 77.4 & 2 \\
            Rank           & 44   & 3 & 77.4 & 2 \\
            Total          & 33   & 3 & 77.4 & 2 \\
            Overall        & 74.9 & 3 & 77.4 & 2 \\
            \hline
        \end{tabular}
        \caption{Results with target-value = true}
        \label{tab:results_true}
    \end{subtable}%
    \hfill
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{gpt4o}} & \multicolumn{2}{c}{\textbf{gpt5}} \\
            & \textbf{Success Rate} & \textbf{SD} & \textbf{Success Rate} & \textbf{SD} \\
            \hline
            Comparison     & -- & -- & -- & -- \\
            Data Retrieval & -- & -- & -- & -- \\
            Difference     & -- & -- & -- & -- \\
            Min/max        & -- & -- & -- & -- \\
            Rank           & -- & -- & -- & -- \\
            Total          & -- & -- & -- & -- \\
            Overall        & -- & -- & -- & -- \\
            \hline
        \end{tabular}
        \caption{Results without target-value}
        \label{tab:results_no_target}
    \end{subtable}
    \caption{Comparison of success rates (with standard deviation) between \textbf{gpt4o} and \textbf{gpt5} across different task categories, reported with and without the use of target-values.}
    \label{tab:results_combined}
\end{table}

@@

Figure~\ref{fig:success_rate_by_category_count} reports the success rate as a function of the number of categories assigned to each expression.
Fluid instructions combining multiple operations were associated with multiple categories.
Results show that the success rate was 75\% for simple expressions (one category), increased to 85\% for two categories,
and dropped to 58\% when three categories were involved.

>>>>

\begin{figure}
    \centering
    \begin{subfigure}{0.48\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/success_rate_by_category}
        \caption{Success rate by Linguistic Category}
        \label{fig:success_rate_by_category}
    \end{subfigure}\hfill
    \begin{subfigure}{0.48\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/success_rate_by_complexity}
        \caption{Success rate by Complexity}
        \label{fig:success_rate_by_complexity}
    \end{subfigure}
    \caption{Success rate of the proposed system, measured over 5 runs with gpt-4o}
    \label{fig:success_rate_comparison}
\end{figure}

@@

    \centering
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{gpt4o}} & \multicolumn{2}{c}{\textbf{gpt5}} \\
            & \textbf{Success Rate (\%)} & \textbf{SD} & \textbf{Success Rate} & \textbf{SD} \\
            \hline
            Comparison     & 74.7   & 3 & 77.4 & 2 \\
            Data Retrieval & 76.4   & 3 & 77.4 & 2 \\
            Difference     & 80.3   & 3 & 77.4 & 2 \\
            Min/max        & 50.2   & 3 & 77.4 & 2 \\
            Rank           & 44.1   & 3 & 77.4 & 2 \\
            Total          & 33.2   & 3 & 77.4 & 2 \\
            Overall        & 74.9 & 3 & 77.4 & 2 \\
            \hline
        \end{tabular}
        \caption{Results with target-value = true}
        \label{tab:results_true}
    \end{subtable}%
    \hfill
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{gpt4o}} & \multicolumn{2}{c}{\textbf{gpt5}} \\
            & \textbf{Success Rate (\%)} & \textbf{SD} & \textbf{Success Rate} & \textbf{SD} \\
            \hline
            Comparison     & -- & -- & -- & -- \\
            Data Retrieval & -- & -- & -- & -- \\
            Difference     & -- & -- & -- & -- \\
            Min/max        & -- & -- & -- & -- \\
            Rank           & -- & -- & -- & -- \\
            Total          & -- & -- & -- & -- \\
            Overall        & -- & -- & -- & -- \\
            \hline
        \end{tabular}
        \caption{Results without target-value}
        \label{tab:results_no_target}
    \end{subtable}
    \caption{Comparison of success rates (with standard deviation) between \textbf{gpt4o} and \textbf{gpt5} across different task categories, reported with and without the use of target-values.}
    \label{tab:results_combined}
\end{table}

@@

Figure~\ref{fig:success_rate_by_complexity} reports the success rate as a function of the number of categories assigned to each expression.
Fluid instructions combining multiple operations were associated with multiple categories.
Results show that the success rate was 75\% for simple expressions (one category), increased to 85\% for two categories,
and dropped to 58\% when three categories were involved.
